### 2015-03-05 appendices.tex
updated case study availability
updated schedule in the case study

        Some diagnostic plots for the baseline quality function
        can be seen in Figure \ref{fig:quality-diag}.  The normal probability plot,
        a.k.a. QQ Plot, shows the errors are not exactly normally distributed, but
        the baseline quality function had good predictive power as shown by the
        high $R^2$. The fitted versus
        residuals plot indicates a lack of heteroscedasticity.  
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.3]{images/quality_diag.png}
            \caption{QUALITY DIAGNOSTIC PLOTS}
            \label{fig:quality-diag}
        \end{figure}

@@

@@

>>>>

        Some diagnostic plots for the baseline quality function
        can be seen in Figure \ref{fig:quality-diag}.  The normal probability plot,
        a.k.a. QQ Plot, shows the errors are not exactly normally distributed, but
        the baseline quality function had good predictive power as shown by the
        high $R^2$. The fitted versus
        residuals plot indicates a lack of heteroscedasticity.  
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.25]{images/quality_diag.png}
            \caption{QUALITY DIAGNOSTIC PLOTS}
            \label{fig:quality-diag}
        \end{figure}

@@

    \subsection{BAR CHART - R CODE}
        This is a code for generating a bar chart.  It is used for reporting
        the scores of all the elements.
        \lstinputlisting[language=R, label=src:barchart]{source/barchart.R}

@@

    \subsection{AVAILABILITY SCORES - R CODE}
        \lstinputlisting[language=R, label=src:availability]{source/availability.R}

    \subsection{REQUIREMENTS SCORES - R CODE}
        \subsubsection{REQUIREMENTS HISTOGRAM}
        \label{app:requirements-hist}
            Figure \ref{fig:req-hist} shows a histogram of the data
            for requirements.  The histogram is based upon the
            fraction $\frac{Scheduled Requirements}{Actual Requirements}$. The
            values where the fraction equals 1 have been left out of the histogram.
            So, the histogram show only the data that did not deliver exactly
            on the number of requirements. Rarely are more requirements actually 
            delivered than what was scheduled.  On the opposite side, the histogram
            bars shrink as they approach zero indicating that it is more common
            to miss a few requirements than all the requirements.

            \begin{figure}[ht]
                \centering
                \includegraphics[scale=.3]{images/req_hist.png}
                \caption{REQUIREMENTS DATA HISTOGRAM (ACTUAL/SCHEDULED)}
                \label{fig:req-hist}
            \end{figure}

        \subsubsection{REQUIREMENTS R CODE}
        \lstinputlisting[language=R, label=src:requirements]{source/requirements.R}

### 2015-03-05 paper_10_intro.tex
updated schedule in the case study

    This work 
    provides a technique for a software development organization to create
    a single number score which indicates the overall performance
    of the organization. The
    score is based upon data collected for 5 result indicators
    of a software development organization: quality, availability,
    satisfaction, schedule, and requirements.  It is not meant
    to be comparative between organizations, but to 
    form a historical baseline for a specific organization.

@@

    The remainder of this dissertation is divided into 5 chapters.  The next chapter provides
    an overview of software, software development lifecycles, software engineering, and software
    development organizations.  Chapter 3 introduces what is meant by the term data-driven
    software engineering. Chapter 4 then provides an explanation of the Cumulative
    Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well
    as the formulas, framework, and data necessary to produce the CRI. Chapter 5 provides
    a technological framework for generating and storing the current and historical CRI values.
    Chapter 6 demostrates how CRI can be implemented in a software development portion of 
    a large financial institution.  Chapter 7 concludes the dissertation with a summary
    of the results and some possible future directions for further enhancements.

>>>>

    This work 
    provides a technique for a software development organization to create
    a single number score which indicates the overall performance
    of the organization. The
    score is based upon data collected for 5 key result indicators
    of a software development organization: quality, availability,
    satisfaction, schedule, and requirements.  It is not meant
    to be comparative between organizations, but to 
    form a historical baseline for a specific organization.  The single
    number is targeted for upper-level management whom need a quick
    and simple strategy to evaluate the performance of the organization.

@@

    The remainder of this dissertation is divided into 7 chapters.  Chapter 2 provides
    an overview of software, software development life cycles, software engineering, and software
    development organizations.  Chapter 3 introduces some existing techniques for measuring
    a software development organization. Chapter 4 then provides an explanation of the Cumulative
    Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well
    as the formulas, framework, and data necessary to produce the CRI. Chapter 5 provides
    a technological framework for storing the current and historical CRI values.
    Chapter 6 demostrates how CRI can be implemented in a software development portion of 
    a large financial institution. Chapter 7 discusses some possible future directions 
    for further enhancements. Chapter 8 concludes the dissertation with a summary
    of the results.

### 2015-03-05 paper_70_case-study.tex
updated schedule in the case study

        \subsubsection{SCHEDULE}
        \subsubsection{REQUIREMENTS}
        \label{sec:case-req}
            There were 15 rows of data that contained 0 for both
            scheduled and actual
            \begin{longtable}{@{}l rr rrr}
                \toprule%
                 \centering%
                 {\bfseries Column}
                 & {\bfseries Min}
                 & {\bfseries Max}
                 & {\bfseries Median}
                 & {\bfseries Mean}
                 & {\bfseries Variance} \\

@@

                Scheduled & 0 & 1.0 & 1.0 & 0.9745 & 0.023 \\
                \myrowcolour%
                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\
                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\

@@

                \multicolumn{6}{c}{476 obs. from 402 Project IDs from 2010 to 2015} \\

@@

>>>>

        \subsubsection{SCHEDULE}
            Figure \ref{tab:schedule_desc} displays some descritive statistics
            for the schedule data.  Since the data is mostly dates, the 
            descriptive statistics are limited, so extra values were
            added to the table after removing 4 outliers.  The new values
            in the table are: Schedule Duration (Scheduled Finish - Scheduled Start),
            Difference (Actual Finish - Schedule Finish), and 
            $\Delta$ ($frac{\Delta}{\text{Schedule Duration}}$ ).

            \begin{longtable}{@{}l rr rrr}
                \toprule%
                 \centering%
                 {\bfseries Column}
                 & {\bfseries Min}
                 & {\bfseries Max}
                 & {\bfseries Median}
                 & {\bfseries Mean} \\

@@

                Scheduled Start & 2013-06-23 & 2015-01-24 & 2014-03-17 & 2014-04-01 \\
                \myrowcolour%
                Scheduled Finish & 2014-01-31 & 2015-01-25 & 2014-08-08 & 2014-08-02 \\
                Actual Start & 2013-01-07 & 2014-10-17 & 2014-01-15  & 2014-02-10 \\
                \myrowcolour%
                Actual Finish & 2014-02-20 & 2014-12-31 & 2014-08-31 & 2014-08-11 \\
                Schedule Duration & 8 & 480 & 92 & 137.7 \\
                \myrowcolour%
                Difference & -283 & 149 & 0.0 & -8.919 \\
                $\Delta$ & -4.75 & 0.6564 & 0.0 & -0.2641 \\

@@

                \multicolumn{5}{c}{41 obs. from 40 Project IDs from mid 2013 to 2015} \\

                \caption{SCHEDULE DATA DESCRIPTIVE STATISTICS}
                \label{tab:schedule_desc}
            \end{longtable}

            The first task with the schedule data is fitting the data to 
            a distribution.  Figure \ref{fig:schedule-hist} shows
            a plot of the histogram of the $\Delta$s and a
            Cauchy curve with location = 0.0 and scale = 0.057.  The Cauchy
            distribution appears to be a good fit.

            \begin{figure}[ht]
                \centering
                \includegraphics[scale=.25]{images/schedule_hist.png}
                \caption{SCHEDULE DATA HISTOGRAM WITH CAUCHY}
                \label{fig:schedule-hist}
            \end{figure}

            Now that the distribution has been identified, the next step
            is determining the Cumulative Distribution Function (C.D.F.)
            for the distribution.  For Cauchy, the general C.D.F. is 
            given as follows.
            \[
                C.D.F. = \frac{1}{\pi}\arctan{\frac{x-x_0}{\gamma}} + \frac{1}{2}
            \]
            where 
            \begin{itemize}
                \item $x_0$ is the location
                \item $\gamma$ is the scale
            \end{itemize}

            Referencing Equation \ref{eq:CDF}, the schedule formula
            for individual project IDs becomes.
            \[
               S_{4_i} = \frac{200}{\pi}\arctan{\left(\frac{\Delta_i}{0.057} \right)} 
            \]

            The CRI schedule scores can be seen in Figure \ref{fig:schedule-scores}.
            These scores appear more eratic than the other elements.
            This difference is due to the small number of releases every month.

            \begin{figure}[ht]
                \centering
                \includegraphics[scale=.3]{images/schedule_scores.png}
                \caption{CRI SCHEDULE SCORES}
                \label{fig:schedule-scores}
            \end{figure}

        \subsubsection{REQUIREMENTS}
        \label{sec:case-req}
            The data for requirements is actually counts of story points
            instead of requirements.  That is because story points
            are a better choice for counting, since they are more
            uniform in size than raw requirements.  Also, the data
            contained 15 rows of data with a 0 for the number of
            scheduled requirements.  Those 15 rows were removed.
            Table \ref{tab:requirements_desc} shows some descriptive
            statistics for the remaining rows. A histogram for the
            data can be seen in Appendix \ref{app:requirements-hist}.

                Scheduled Requirements & 0.5 & 1248 & 75.5 & 136.9 & 31243.89 \\
                \myrowcolour%
                Actual Requirements & 0 & 1247 & 58 & 123.8 & 30844.75 \\
                $\frac{Actual Requirements}{Scheduled Requirements}$ & 0 & 1.2364 & 1.0 & 0.8515 & 0.05 \\

                \multicolumn{6}{c}{461 obs. from 402 Project IDs from 2010 to 2015} \\

@@

            \begin{figure}[ht]
                \centering
                \includegraphics[scale=.3]{images/requirements_scores.png}
                \caption{CRI REQUIREMENTS SCORES}
                \label{fig:requirements-scores}
            \end{figure}

            Figure \ref{fig:requirements-scores} displays the CRI requirements
            scores. The scores are as expected considering the histogram. Many
            of the projects meet the requirements exactly, and when the requirements
            are not met, it is usually by a small number.
            Thus the scores are all 0 or slightly below.
